Two NIRCam channels are Better than One: How JWST Can Do More Science with NIRCam's Short-Wavelength Dispersed Hartmann Sensor

### 2016-10-05 ms.tex
This is the version I will submit after the first referee report. I got rid of the bibliographystyle astroads that I originally had in there since it doesn't seem to be used nor is recognized by PASP's system.
I renamed the NIRCam+OTE file name because the PASP submission system doesn't like the plus sign in the file name.
Got rid of all of Mike's bazillion affiliations since he's now at ASU.

\usepackage{natbib}
\bibliographystyle{astroads}

@@

\author{M. Line\altaffilmark{1,2,3,4}}
\affil{Department of Astronomy and Astrophysics, University of California, Santa Cruz, CA 95064}

@@

\altaffiltext{1}{Hubble Postdoctoral Fellow}
\altaffiltext{2}{NASA Ames Research Center, Moffett Field, CA 94035}
\altaffiltext{3}{Bay Area Environmental Research Institute, Petaluma, CA}
\altaffiltext{4}{School of Earth and Space Exploration, Arizona State University, Tempe, AZ}

@@

\begin{figure}
\centering
\includegraphics[width=1.0\columnwidth]{NIRCam+OTE_SWA_DHS_and_F150W2_efficiency.pdf}
\caption{Throughput as a function of wavelength for the DHS grism, F150W2 filter and F200W filter that includes the telescope and instrument transmission. The total throughput is the product of the filter curve, ``DHS'' grism and the pupil area fraction from Table~\ref{tab:pupfrac}..}\label{fig:DHSthrough}
\end{figure}

>>>>

\usepackage{natbib}

@@

\author{M. Line}
\affil{School of Earth and Space Exploration, Arizona State University, Tempe, AZ 85281}

@@

@@

\begin{figure}
\centering
\includegraphics[width=1.0\columnwidth]{NIRCam_OTE_SWA_DHS_and_F150W2_efficiency.pdf}
\caption{Throughput as a function of wavelength for the DHS grism, F150W2 filter and F200W filter that includes the telescope and instrument transmission. The total throughput is the product of the filter curve, ``DHS'' grism and the pupil area fraction from Table~\ref{tab:pupfrac}..}\label{fig:DHSthrough}
\end{figure}
